Spectroscopic confirmation of very-wide binaries and large-separation comoving pairs from \textsl{Gaia DR1}

### 2017-07-27 paper/comoving-followup.tex

Typically, high-order standard polynomials or Chebyshev polynomials are used to
fit for the wavelength dispersion function.
We found that using such functions can lead to vastly incorrect wavelength
values near either end of the pixel grid where the polynomial function is
un- or weakly-constrained.
\smoh{We instead use a combined linear polynomial + GP to model the wavelength
  dispersion. - what is each component supposed to capture?}
We again use a Mat\'ern 3/2 kernel, use \lbfgsb\ optimization, and convert any
scale parameter to log-space before maximizing the log-likelihood.
\figurename~\ref{fig:wavelength-GP} shows an example of the residuals from one
such fit; black points show the (pixel-centroid, wavelength) pairs with the
best-fit model subtracted.
The envelope around zero (shaded region, orange) shows the variance of the GP
model projected into the data space; when the GP variance is large, the
pixel-to-wavelength mapping is uncertain.
We therefore only use the pixel range from 250--1210, corresponding to a
wavelength range of $\approx 5500$--$7400~{\rm \AA}$; gray shaded region shows
the excluded pixel/wavelength ranges.
\smoh{The wavelength solution is not well constrained no matter what (due to
  lack of data), and using GP model instead of polynomials does not change
  that. Instead, it seems to me that GP model informs us of the regions to
  discard.  Thus, technically, I think ``We instead use ...'' is not correctly
  justified. Modify at will. Obviously quite a minor point..}

>>>>

Typically, high-order standard polynomials or Chebyshev polynomials are used to
fit for the wavelength dispersion function.
We found that using such functions can lead to vastly incorrect wavelength
values near either end of the pixel grid where the polynomial function is
un- or weakly-constrained.
\smoh{We instead use a combined linear polynomial + GP to model the wavelength
  dispersion. - what is each component supposed to capture?}
We again use a Mat\'ern 3/2 kernel, use \lbfgsb\ optimization, and convert any
scale parameter to log-space before maximizing the log-likelihood.
\figurename~\ref{fig:wavelength-GP} shows an example of the residuals from one
such fit; black points show the (pixel-centroid, wavelength) pairs with the
best-fit model subtracted.
The envelope around zero (shaded region, orange) shows the variance of the GP
model projected into the data space; when the GP variance is large, the
pixel-to-wavelength mapping is uncertain.
We therefore only use the pixel range from 250--1210, corresponding to a
wavelength range of $\approx 5500$--$7400~{\rm \AA}$; gray shaded region shows
the excluded pixel/wavelength ranges.
\smoh{The wavelength solution is not well constrained at either end no matter
  what (due to lack of data), and using GP model instead of polynomials does
  not change that. Instead, it seems to me that GP model informs us of the
  regions to discard.  Thus, technically, I think ``We instead use ...'' is not
  correctly justified. Modify at will. Obviously quite a minor point..}
